Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
edits

We imagine integrated activity diaries to be used by both clinicians
and patients in several ways.  First, for nearly all types of
conditions, monitoring a person's overall daily activity and sleep
duration could easily indicate how much rest, exercise, exposure to
others, and the outside world they might be getting.  Daily
records of the time(s) that a person gets up, eats, works, exercises
and relaxes can be analysed by clinicians for irregular behaviours or
habits that might be affecting a person's well-being. For more
specific conditions, daily measurements of a person's blood pressure,
blood oxidation, heart rate, breathing, weight, and galvanic skin
response could be useful for tracking progress on a prescribed
intervention, recovery from an illness, or onset of a new conditions,
for example, or be used to pinpoint sources of prolonged stress.

@@

Since SNOWMED-CT nor ICD cover activity-related concepts, we devised a supplemental ontology called \emph{Activity-SENSE}.  This ontology encompasses patient activities, and standard units of measure with which activities measurements were taken, and concepts for describing sensors used.  The intention is for records in Activity-SENSE, like those of SNOMED-CT, will be eventually translatable to dozens of different languages and mapped to similar activity ontologies, allowing international use and greater operability.

>>>>

We imagine integrated activity diaries to be used by both clinicians
and patients in several ways.  First, for nearly all types of
conditions, monitoring a person's overall daily activity and sleep
duration could easily indicate how much rest, exercise, and social
exposure they might be getting.  Moreover, longitudinal records of the
time(s) that a person gets up, eats, works, exercises and relaxes can
be analysed for irregular behaviours or habits that might be affecting
their well-being. For more specific conditions, daily
measurements of a person's blood pressure, blood oxidation, heart
rate, breathing, weight, and galvanic skin response could be useful
for tracking progress on a prescribed intervention, recovery from an
illness, or onset of a new conditions, for example, or be used to
pinpoint sources of prolonged stress.

@@

Since SNOWMED-CT nor ICD-10 cover activity-related concepts, we devised a supplemental ontology called \emph{Activity-SENSE}.  This ontology encompasses patient activities, and standard units of measure with which activities measurements were taken, and concepts for describing sensors used.  The intention is for records in Activity-SENSE, like those of SNOMED-CT, will be eventually translatable to dozens of different languages and mapped to similar activity ontologies, allowing international use and greater operability.
